Non-additive measures for quantum probability?

### 2024-05-20 Proceedings/2024-IPMU/carcassi-quantummeasure.tex
IPMU2024: adding last citation

\keywords{non-additive set functions, quantum physics, statistical mechanics, information theory}
\end{abstract}
%
\section{Introduction}
%
It is well-established that quantum probability does not follow classical Kolmogorov probability calculus. Various approaches have been developed to loosen the axioms, of which the use of signed measures is the most successful (e.g. the Wigner quasiprobability distribution).\cite{gleason1957measures,groenewold1946principles,gudder2009quantum,hamhalter2003quantum,monchietti2023measure,moyal1949quantum,sorkin1994quantum,svozil2022extending} On the other hand, the use of non-additive measures (i.e. set functions) has received little attention, which is striking for two reasons. First, we have found that non-additive measures emerge quite naturally in quantum mechanics when looking for a quantum analogue of count of states\cite{aop-phys-QuantumRequiresNonAdditiveMeasures}, which plays a fundamental role in statistical mechanics. Second, there has been an increased use of quantum probability in non-classical decision making CITE, an area where non-additive measure theory is widely used.

>>>>

\keywords{non-additive set functions, quantum physics, statistical mechanics, information theory}
\end{abstract}
%
\section{Introduction}
%
It is well-established that quantum probability does not follow classical Kolmogorov probability calculus. Various approaches have been developed to loosen the axioms, of which the use of signed measures is the most successful (e.g. the Wigner quasiprobability distribution).\cite{gleason1957measures,groenewold1946principles,gudder2009quantum,hamhalter2003quantum,monchietti2023measure,moyal1949quantum,sorkin1994quantum,svozil2022extending} On the other hand, the use of non-additive measures (i.e. set functions) has received little attention, which is striking for two reasons. First, we have found that non-additive measures emerge quite naturally in quantum mechanics when looking for a quantum analogue of count of states\cite{aop-phys-QuantumRequiresNonAdditiveMeasures}, which plays a fundamental role in statistical mechanics. Second, there has been an increased use of quantum probability in non-classical decision making\cite{quantumrev2023}, an area where non-additive measure theory is widely used.
